New Foundations and Fitness of Algebraic File Synchronization

### 2016-01-03 2015/abstract.tex
New title, keywords, MSC, ACM classes

With distributed computing and mobile applications,
synchronizing divergent replicas of data is a more and more common problem.
We investigate an operation-based approach to filesystem synchronization
and further our theoretical understanding of this problem
by presenting rigorous algebraic proofs that the algorithms desribed for
update detection and reconciliation return working solutions
that cannot be improved on.

>>>>

With distributed computing and mobile applications,
synchronizing divergent replicas of data is a more and more common problem.
We investigate an operation-based approach to filesystem synchronization
and further our theoretical understanding of this problem
by presenting rigorous algebraic proofs that the algorithms described for
update detection and reconciliation return working solutions
that cannot be improved on.

### 2016-01-03 2015/paper.tex
Reordering; improvements; new notation; improved figure
More improvements
Added abstract
Added contact info
Capitalised references
New title, keywords, MSC, ACM classes

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{centernot}
\usepackage{tikz}
\usepackage{cleveref}

@@

\title{Complete Algebraic File Synchronization}
\author{Elod Pal Csirmaz}

\begin{document}
\maketitle
\begin{abstract}
Abstract goes here
\end{abstract}

\input{intro}

@@

\input{axioms}

@@

\input{comparisons}

\section{Further Research}

TODO: next steps. multiple replicas

\input{algebra}

\section{Conclusions}

% TODO
Conclusions go here

>>>>

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{centernot}
\usepackage{tikz}
\usepackage[capitalise]{cleveref}

@@

% fitness, validity, integrity, well-founded
% foundation, groundwork
\title{New Foundations and Fitness of Algebraic File Synchronization}
\author{Elod Pal Csirmaz\\
\texttt{\rot{\rot{maz.}{csir}{ep}com}{@}{elod}}}

\begin{document}
\maketitle
\begin{abstract}

\input{abstract}

\bigskip\noindent
{\bf Keywords:} % (4-6)
file synchronization,
algebraic approach,
distributed systems,
reconciliation,
data replication
% conflict detection,
% operation-based 
% conflict resolution
% computer algebra

\bigskip\noindent
{\bf MSC classes:} % http://www.ams.org/mathscinet/msc/msc2010.html
08A70, % Applications of universal algebra in computer science
68M07, % Mathematical problems of computer architecture
68M14, % Distributed systems
68P05, % Data structures
68P20 % Information storage and retrieval
% 68N25         Operating systems

\bigskip\noindent
{\bf ACM classes:} % http://www.acm.org/about/class/ccs98-html
% (D) Software (D.4) Operating systems
D.4.3, % File systems management
% (E) Data
E.5, % Files
% (F) Theory of computation (F.2) ANALYSIS OF ALGORITHMS AND PROBLEM COMPLEXITY
F.2.2, % Nonnumerical Algorithms and Problems
% (G) Mathematics of Computing
G.2 % DISCRETE MATHEMATICS
% (H) Information Systems (H.3) INFORMATION STORAGE AND RETRIEVAL
% H.3.4 % Systems and Software

\end{abstract}

% section
\input{intro}

@@

% section
\input{axioms}

@@

% section
\input{comparisons}

% section
\input{algebra}

% section
\input{conclusion}
